Proof of concept

### 2022-12-21 docs/src/paper/experiments/_real_world.qmd
uh

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble
]
generators = Dict(
    :Greedy=>GreedyGenerator(), 
    :Generic=>GenericGenerator(),
    :REVISE=>REVISEGenerator(),
    :DICE=>DiCEGenerator(),
)
```

>>>>

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble
]
generators = Dict(
    # :Greedy=>GreedyGenerator(), 
    # :Generic=>GenericGenerator(),
    :REVISE=>REVISEGenerator(),
    # :DICE=>DiCEGenerator(),
)
```
